Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-08-17 revised-chapter.tex
Revisions: Added Conclusion section

@@

>>>>

Since a GP model expresses prior assumptions about the finite
dimensional distribution of the quantitiy of interest, the expression
for $Q(\theta)$ follows directly from the expression of the
probability density function of a multivariate gaussian.

@@

\section{Conclusion}

In this chapter, we introduced the reader to the \emph{Gaussian
  Process} prediction methodology in the context of space weather forecasting.

In order to successfully apply a Gaussian Process model for a
prediction problem, there are a number of design choices which the
modeler must take. These include choice of model trend, kernel, and
hyperparameter selection among others, we gave a detailed
description of each step of the process from the data to a operational
Gaussian Process forecast model.

To eludicate each step of the modeling workflow, we
considered as an example, one hour ahead prediction of the Dst
index.

We demonstrated that in the one hour ahead Dst prediction
context GP models yield reliable probabilistic predictions with
relatively small data sizes: the training set contains 243
instances, while the validation set contains 782 instances.

To understand how well the models perform, their performance is
compared with the trivial one hour ahead baseline; the
\emph{persistence model}. The GP-AR and GP-ARX both improved on the
performance of the \emph{persistence model}.

\emph{Gaussian Processes} present the data driven space weather practitioner with
a tractable and expressive method for generating probabilistic
forecasts of geomagnetic time series. Leveraging the strengths of the
Bayesian approach, they are able to learn robust predictors from data.
